Supplement

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
Update Supplement.Rmd

## Test for normal distribution of predictor variables

@@

>>>>

## Test for normal distribution of predictor variables {#SupplementNV}

@@

## Post-hoc tests of strategies for effects of ER on subjective arousal and physiological responding {#SupplementEffectER}

``` {r SupplEffectER, echo=FALSE, message=FALSE, warning=FALSE} 
papaja::apa_table(
  SubjArousalReg_con,
  caption = "Post-hoc tests for effects of ER strategies on subjective arousal ratings.",
  escape = FALSE,
  placement = "H",
  format.args = list(format = "e"))

papaja::apa_table(
  EMGCorrReg_con,
  caption = "Post-hoc tests for effects of ER strategies on Corrugator activity",
  escape = FALSE,
  placement = "H",
  )

papaja::apa_table(
  EMGLevReg_con,
  caption = "Post-hoc tests for effects of ER strategies on Levator activity",
  escape = FALSE,
  placement = "H")
